`r glue::glue('Doublet benchmarking results: {params$dataset}')`

### 2024-05-29 analyses/doublet-detection/template-notebooks/02_explore-benchmark-results.Rmd
table printing

```{r functions}
plot_pca_d <- function(df, color_column, color_lab) {
  # Plot PC with a discrete color variable, showing doublets on top
  # df is expected to contain columns PC1, PC2, and `color_column`
  # The `color_column` argument should _not_ be provided as a string
  ggplot(doublet_df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(alpha = 0.5) + 
  scale_color_manual(values = c("black", "lightblue")) + 
  # ensure doublets are on top for visibility
  geom_point(
    data = dplyr::filter(doublet_df, {{color_column}} == "doublet"), 
    color = "black"
  ) + 
  labs(color = color_lab) + 
  theme(
    legend.title.position = "top",
    legend.position = "bottom"
  )
}

@@

plot_jitter_scores <- function(df, score_col, pred_col, method_name){
  # Plot jitter plot of score distributions and predictions, colored by ground truth
  # df is expected to contain columns `ground_truth`, `score_col`, and `pred_col`
  # The column arguments should _not_ be provided as strings
  ggplot(df) +
    aes(x = ground_truth,
        y = {{score_col}}, 
        color = {{pred_col}}) + 
    geom_jitter(
      alpha = 0.2, 
      width = 0.1
    ) + 
    labs(
      x = "Ground truth call",
      y = glue::glue("{method_name} score"),
      color = glue::glue("{method_name} prediction")
    ) + 
  theme(
    legend.title.position = "top",
    legend.position = "bottom"
  )
}

@@

```{r}
dub_table <- table(doublet_df$ground_truth)

dub_percent <- round(dub_table[["doublet"]]/sum(dub_table), 2) * 100
dub_table
```
`r dub_percent`% of droplets in this dataset are doublets.

@@

```{r}
table(doublet_df$scdbl_prediction)
```

@@

@@

@@

@@

>>>>

```{r functions}
print_doublet_table <- function(df, pred_col, is_ground_truth = FALSE) {
  # Function to print a table of doublet counts and a sentence stating the percentage of doublets
  # df is expected to contain `pred_col`, should should be provided as a string
  dub_table <- table(df[[pred_col]])
  dub_percent <- round(dub_table[["doublet"]]/sum(dub_table), 4) * 100

  print(dub_table)

  if (is_ground_truth) {
    output <- glue::glue("{dub_percent}% of droplets in this dataset are doublets.") 
  } else {
    output <- glue::glue("{dub_percent}% of droplets in this dataset were predicted to be doublets.")
  }

  return(output)
}

plot_pca_d <- function(df, color_column, color_lab) {
  # Plot PC with a discrete color variable, showing doublets on top
  # df is expected to contain columns PC1, PC2, and `color_column`
  # The `color_column` argument should _not_ be provided as a string
  ggplot(doublet_df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(alpha = 0.5) + 
  scale_color_manual(values = c("black", "lightblue")) + 
  # ensure doublets are on top for visibility
  geom_point(
    data = dplyr::filter(doublet_df, {{color_column}} == "doublet"), 
    color = "black"
  ) + 
  labs(color = color_lab) + 
  theme(
    legend.title.position = "top",
    legend.position = "bottom"
  )
}

@@

plot_jitter_scores <- function(df, score_col, pred_col, method_name){
  # Plot jitter plot of score distributions and predictions, colored by ground truth
  # df is expected to contain columns `ground_truth`, `score_col`, and `pred_col`
  # The column arguments should _not_ be provided as strings
  ggplot(df) +
    aes(x = ground_truth,
        y = {{score_col}}, 
        color = {{pred_col}}) + 
    geom_jitter(
      alpha = 0.2, 
      width = 0.1
    ) + 
    labs(
      x = "Ground truth",
      y = glue::glue("{method_name} score"),
      color = glue::glue("{method_name} prediction")
    ) + 
  theme(
    legend.title.position = "top",
    legend.position = "bottom"
  )
}

@@

```{r}
percent <- print_doublet_table(doublet_df, "ground_truth", is_ground_truth = TRUE)
```

```{r results = "asis"}
percent
```

@@

```{r}
percent <- print_doublet_table(doublet_df, "scdbl_prediction")
```

```{r results = "asis"}
percent
```

@@

```{r}
percent <- print_doublet_table(doublet_df, "scrublet_prediction")
```

```{r results = "asis"}
percent
```

@@

```{r}
percent <- print_doublet_table(doublet_df, "cxds_prediction_0.5")
```

```{r results = "asis"}
percent
```

@@

```{r}
percent <- print_doublet_table(doublet_df, "cxds_prediction_0.75")
```

```{r results = "asis"}
percent
```

@@

```{r}
percent <- print_doublet_table(doublet_df, "cxds_prediction_0.9")
```

```{r results = "asis"}
percent
```
